Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
one more pass over abstract, use trick to avoid period spacing with project name

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co.\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

\begin{abstract}
  \Hydras is a collaborative library of discrete mathematics,
  written for the \coq proof assistant and developed as part
  of the \community project on GitHub. The Coq code is accompanied
  by an electronic book, generated with the help of the \alectr
  literate proving tool. We present the evolution of the mathematical
  contents of the library since former presentations at JFLA meetings.
  Then, we describe how the structure of the project is determined
  by two requirements which must be continuously satisfied.
  First, the Coq code needs to be compatible with its ever-evolving
  dependencies (the Coq proof assistant and several Coq packages both from
  inside and outside \community) and its reverse dependencies (\community
  projects that depend on it). Second, the book needs to be consistent
  with the library Coq code, which undergoes frequent changes to improve
  structure and include new definitions and results.
\end{abstract}

@@

While books that document proof assistant libraries are valuable to beginners, the purpose of current books is mainly instrumental, i.e., to teach a certain topic or technique. We believe that such books can become \emph{ends in themselves}---not just sources of learning, but also sources of inspiration and entertainment.

>>>>

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
%\newcommand{\Hydras}{Hydra-battles\xspace}

@@

\begin{abstract}
  \Hydras is a collaborative library of discrete mathematics for the
  \coq proof assistant, developed as part of the \community project
  on GitHub. The Coq code is accompanied
  by an electronic book, generated with the help of the \alectr
  literate proving tool. We present the evolution of the mathematical
  contents of the library since former presentations at JFLA meetings.
  Then, we describe how the structure of the project is determined
  by two requirements which must be continuously satisfied.
  First, the Coq code needs to be compatible with its ever-evolving
  dependencies (the Coq proof assistant and several Coq packages both from
  inside and outside \community) and its reverse dependencies (\community
  projects that depend on it). Second, the book needs to be consistent
  with the Coq code, which undergoes frequent changes to improve
  structure and include new definitions and results. We believe \Hydras demonstrates
  that books on formalized mathematics are not limited to
  providing exposition of theories and reasoning techniques---they
  can also provide inspiration and entertainment that transcends educational goals.
\end{abstract}

@@

While books that document proof assistant libraries are valuable to beginners, the purpose of recently published books is mainly instrumental, i.e., to teach a certain topic or technique. We believe that books can instead become \emph{ends in themselves}---not just sources of learning, but also sources of inspiration and entertainment.
